A replication of a simulation study on measuring and correcting bias of under-5 mortality estimation in populations affected by HIV/AIDS

### 2020-02-24 analysis/paper.Rmd
add one reference

## Simulation Construction

@@

The figure 4 (Fig. \@ref(fig:ori-fig-4)) and 5 (Fig. \@ref(fig:ori-fig-5)) in the original article were created by applying the best-performing model as well as an independent model (REF) to empirical data from 2010 DHS for Malawi and Tanzania respectively to estimate U5M of different age groups of population. By comparing differences in U5M estimates of unadjusted data and adjusted data by two models, the authors suggested that the new model was able to correct the bias from indirect estimates.

@@

```{r, rep-fig-4, fig.cap="Replication of figure 4 with new simulation data", echo=FALSE, fig.align='center'}

@@

```{r, rep-fig-5, fig.cap="Replication of figure 5 with new simulation data", echo=FALSE, fig.align='center'}

>>>>

@@

The figure 4 (Fig. \@ref(fig:ori-fig-4)) and 5 (Fig. \@ref(fig:ori-fig-5)) in the original article were created by applying the best-performing model as well as an independent model [@ward2008effect] to empirical data from 2010 DHS for Malawi and Tanzania respectively to estimate U5M of different age groups of population. By comparing differences in U5M estimates of unadjusted data and adjusted data by two models, the authors suggested that the new model was able to correct the bias from indirect estimates.

@@

```{r, rep-fig-4, fig.cap="Replication of figure 4 with new simulation data", echo=FALSE}

@@

```{r, rep-fig-5, fig.cap="Replication of figure 5 with new simulation data", echo=FALSE}
